Effects of CHILDREN's programs

### 2020-02-23 paper.Rnw

<<echo=FALSE, results='asis', message=FALSE>>=
lm1_selfworth = readRDS("./ANALYSIS/Tables/lm1_selfworth.Rds")
lm2_selfworth = readRDS("./ANALYSIS/Tables/lm2_selfworth.Rds")
lm3_selfworth = readRDS("./ANALYSIS/Tables/lm3_selfworth.Rds")
lm4_selfworth = readRDS("./ANALYSIS/Tables/lm4_selfworth.Rds")

table1_selfworth <- stargazer(lm1_selfworth,
                    lm2_selfworth,
                    lm3_selfworth,
                    lm4_selfworth,
          title = "Regression Results",
          order = c('Constant', 'treatEF'),
          omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
                   'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
                   'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
                   'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
                   'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
                   'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
                   'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
                   'dummy_2018', 'id'
                  ),
          add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
                           c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
          align = TRUE,
          float.env = "sidewaystable")
# row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")
# colnames(tableDispSumm) <- c("$Corr(X_t, X_{t-1})$", "$\\sigma(X)$", "$\\frac{\\sigma(X)}{\\sigma(Y)}$", "$\\frac{\\sigma(X)}{\\sigma(GDP)}$")
# tableDispSumm <- xtable(tableDispSumm, caption = "Productivity dispersion: Summary statistics", digits = 3, align = "crccc")
# print(tableDispSumm, sanitize.text.function = function(x) {x}, caption.placement = "top")
@

>>>>

<<echo=FALSE, results='asis', message=FALSE>>=

# first, read in all Rds objects that you need

lm1_selfworth = readRDS("./ANALYSIS/Tables/lm1_selfworth.Rds")
lm2_selfworth = readRDS("./ANALYSIS/Tables/lm2_selfworth.Rds")
lm3_selfworth = readRDS("./ANALYSIS/Tables/lm3_selfworth.Rds")
lm4_selfworth = readRDS("./ANALYSIS/Tables/lm4_selfworth.Rds")

table1_selfworth <- stargazer(lm1_selfworth,
                    lm2_selfworth,
                    lm3_selfworth,
                    lm4_selfworth,
          title = "Regression Results",
          order = c('Constant', 'treatEF'),
          omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
                   'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
                   'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
                   'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
                   'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
                   'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
                   'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
                   'dummy_2018', 'id'
                  ),
          add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
                           c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
          align = TRUE,

          # this line of code rotates the table by 90 degrees counterclockwise

          float.env = "sidewaystable")
# row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")
# colnames(tableDispSumm) <- c("$Corr(X_t, X_{t-1})$", "$\\sigma(X)$", "$\\frac{\\sigma(X)}{\\sigma(Y)}$", "$\\frac{\\sigma(X)}{\\sigma(GDP)}$")
# tableDispSumm <- xtable(tableDispSumm, caption = "Productivity dispersion: Summary statistics", digits = 3, align = "crccc")
# print(tableDispSumm, sanitize.text.function = function(x) {x}, caption.placement = "top")
@
